**OptiFit: a fast method for fitting amplicon sequences to existing OTUs**

### 2021-08-30 paper/manuscript.tex
update word document

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\author{}
\date{\vspace{-2.5em}}

@@

\hypertarget{taxonomic-resolution-matters-for-microbiome-based-classification-of-colorectal-cancer}{%
\section{Taxonomic Resolution Matters for Microbiome-Based
Classification of Colorectal
Cancer}\label{taxonomic-resolution-matters-for-microbiome-based-classification-of-colorectal-cancer}}

@@

Courtney R. Armour\({^1}\), Begüm D.Topçuoğlu, Andrea Garretto\({^1}\),
Patrick D. Schloss \({^1}\)\({^*}\)

@@

\({^1}\) Department of Microbiology and Immunology, University of
Michigan, Ann Arbor

@@

\({^*}\) Correspondence: Patrick D. Schloss
\href{mailto:pschloss@umich.edu}{pschloss@umich.edu}

@@

Colorectal cancer is one of the most common cancers in men and women and
a leading cause of cancer related deaths in the United States
(\protect\hyperlink{ref-siegel2020}{1}). Early detection and treatment
are essential to increase survival rates, but for a variety of reasons
including the invasiveness and high cost of screening
(i.e.~colonoscopy), many people do not comply with recommended screening
guidelines (\protect\hyperlink{ref-garcuxeda2011a}{2}) prompting a need
for low cost, non-invasive detection methods. A growing body of research
points to the gut microbiome as a promising target for non-invasive
screening to detect screen relevant neoplasia (SRNs) consisting of
pre-cancerous polyps (i.e.~advanced adenomas) and carcinomas. Efforts to
realize the diagnostic potential of the gut microbiome in detecting SRNs
have focused on machine learning (ML) methods using abundances of
operational taxonomic unit (OTU) classifications based on amplicon
sequencing of the 16S rRNA gene \{\}. However, whether this is the
optimal taxonomic resolution for classifying SRNs from microbiome data
is unknown. Additionally, recent work has pushed for the use of amplicon
sequence variants (ASVs) to replace OTUs for marker-gene analysis
because of the improved resolution with ASVs
(\protect\hyperlink{ref-callahan2017}{3}). However, whether the
additional resolution provided by ASVs is useful for ML classification
is unclear \{\}. Since ML classification relies on consistent
differences between groups, its possible that the resolution at the ASV
level is too individualized to accurately differentiate groups.
Topçuoğlu \emph{et al} (\protect\hyperlink{ref-topuxe7uolu2020}{4})
recently demonstrated how to effectively apply machine learning (ML)
methods to microbiome based classification problems and developed a
framework for applying ML practices in a more reproducible way
(mikropml). This analysis utilizes the reproducible framework developed
by Topçuoğlu \emph{et al} to determine which ML method and taxonomic
level produce the best performing classifier for detecting SRNs from
microbiome data.

@@

While comparing AUROC values between models is a useful way to assess
the overall model performance, they summarize the performance across all
thresholds and can be misleading since models with the same AUROC can
have different ROC curve shapes (\protect\hyperlink{ref-lobo2008}{5}).
Depending on the intended implementation of the model, one may want to
optimize the true-positive rate (or sensitivity) over the false-positive
rate (or 1-specificity), or vice versa. In this case, the optimal model
will detect as many true positives (people with SRNs) as possible. To
further compare the model performance across taxonomic levels we
compared the sensitivity of the models at a specificity of 90\%. The
highest sensitivity values were observed for family, genus, and OTU
level data (Figure 1B), consistent with the AUROC results. Phylum,
class, order, and ASV sensitivity values were all significantly lower
than family, genus, and OTU sensitivity values (Figure 1B). This
analysis further supports the observation that finer resolution is does
not improve SRN detection.

@@

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\textbf{\emph{Data processing.}} Sequence data was processed with mothur
(1.44.3) using the SILVA reference database (v132) to produce count
tables for phylum, class, order, family, genus, OTU, and ASV following
the Schloss Lab MiSeq SOP described on the mothur website. ASV level
data was also produced using DADA2 to ensure consistent results with a
different pipeline. Data was processed following the DADA2 pipeline, but
setting pool=TRUE to infer ASVs from the whole dataset rather than per
sample. The resulting ASV table was subsampled for consistency with the
mothur data. These results were consistent for ASVs generated with DADA2
(\protect\hyperlink{ref-callahan2016}{6}) (mean AUROC: 0.659).

@@

\hypertarget{figures}{%
\subsection{Figures}\label{figures}}

\includegraphics{figure_1.png}

@@

\hypertarget{tables}{%
\subsection{Tables}\label{tables}}

\begin{longtable}[]{@{}lrrc@{}}
\toprule
Taxonomic Level & Number of Features &
\makecell[c]{Number of Features \\ After Preprocessing} &
\makecell[c]{Percent of Features Kept \\ After Preprocessing} \\
\midrule
\endhead
Phylum & 19 & 9 & 47.4 \% \\
Class & 36 & 19 & 52.8 \% \\
Order & 65 & 28 & 43.1 \% \\
Family & 124 & 54 & 43.5 \% \\
Genus & 316 & 115 & 36.4 \% \\
OTU & 20,079 & 705 & 3.5 \% \\
ASV & 104,106 & 478 & 0.5 \% \\
\bottomrule
\end{longtable}

@@

\hypertarget{supplemental-figures}{%
\subsection{Supplemental Figures}\label{supplemental-figures}}

\includegraphics{figure_s1.png}

@@

\includegraphics[width=\textwidth,height=0.5\textheight]{figure_s2.png}

@@

\includegraphics[width=\textwidth,height=0.45\textheight]{figure_s3.png}\\
\textbf{Supplemental Figure 3: Prevalence of Taxa in Samples.}
Distribution of the prevalence of taxa across samples at each taxonomic
level. Percent of samples is split into 10 groups where the first is
taxa present in 0 to 10\% of samples, then \textgreater10\% to 20\% of
samples, and so on. The total number of taxa for each taxonomic level
after preprocessing is in parenthesis next to the title of the plot (the
name of the taxonomic level).

@@

\includegraphics[width=\textwidth,height=0.85\textheight]{figure_s4.png}\\
\textbf{Supplemental Figure 4: Top 10 important taxa at each taxonomic
level.} Summary of the 10 most important taxa for the random forest
models at each taxonomic level based on the average decrease in AUROC
when the feature is permuted.

@@

\hypertarget{references}{%
\subsection*{References}\label{references}}
\addcontentsline{toc}{subsection}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{1}
\leavevmode\hypertarget{ref-siegel2020}{}%
\CSLLeftMargin{1. }
\CSLRightInline{\textbf{Siegel RL}, \textbf{Miller KD}, \textbf{Sauer
AG}, \textbf{Fedewa SA}, \textbf{Butterly LF}, \textbf{Anderson JC},
\textbf{Cercek A}, \textbf{Smith RA}, \textbf{Jemal A}. 2020. Colorectal
cancer statistics, 2020. CA: A Cancer Journal for Clinicians
\textbf{70}:145--164. doi:\url{https://doi.org/10.3322/caac.21601}.}

\leavevmode\hypertarget{ref-garcuxeda2011a}{}%
\CSLLeftMargin{2. }
\CSLRightInline{\textbf{García G}, \textbf{Z A}. 2011. Factors
Influencing Colorectal Cancer Screening Participation. Gastroenterology
Research and Practice \textbf{2012}:e483417.
doi:\href{https://doi.org/10.1155/2012/483417}{10.1155/2012/483417}.}

\leavevmode\hypertarget{ref-callahan2017}{}%
\CSLLeftMargin{3. }
\CSLRightInline{\textbf{Callahan BJ}, \textbf{McMurdie PJ},
\textbf{Holmes SP}. 2017. Exact sequence variants should replace
operational taxonomic units in marker-gene data analysis. The ISME
Journal \textbf{11}:2639--2643.
doi:\href{https://doi.org/10.1038/ismej.2017.119}{10.1038/ismej.2017.119}.}

\leavevmode\hypertarget{ref-topuxe7uolu2020}{}%
\CSLLeftMargin{4. }
\CSLRightInline{\textbf{Topçuoğlu BD}, \textbf{Lesniak NA},
\textbf{Ruffin MT}, \textbf{Wiens J}, \textbf{Schloss PD}. 2020. A
Framework for Effective Application of Machine Learning to
Microbiome-Based Classification Problems. mBio \textbf{11}.
doi:\href{https://doi.org/10.1128/mBio.00434-20}{10.1128/mBio.00434-20}.}

\leavevmode\hypertarget{ref-lobo2008}{}%
\CSLLeftMargin{5. }
\CSLRightInline{\textbf{Lobo JM}, \textbf{Jiménez-Valverde A},
\textbf{Real R}. 2008. AUC: a misleading measure of the performance of
predictive distribution models. Global Ecology and Biogeography
\textbf{17}:145--151.
doi:\href{https://doi.org/10.1111/j.1466-8238.2007.00358.x}{10.1111/j.1466-8238.2007.00358.x}.}

\leavevmode\hypertarget{ref-callahan2016}{}%
\CSLLeftMargin{6. }
\CSLRightInline{\textbf{Callahan BJ}, \textbf{McMurdie PJ},
\textbf{Rosen MJ}, \textbf{Han AW}, \textbf{Johnson AJA}, \textbf{Holmes
SP}. 2016. DADA2: High-resolution sample inference from Illumina
amplicon data. Nature Methods \textbf{13}:581--583.
doi:\href{https://doi.org/10.1038/nmeth.3869}{10.1038/nmeth.3869}.}

\end{CSLReferences}

>>>>

\documentclass[]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\author{}
\date{\vspace{-2.5em}}
\usepackage{helvet}
\renewcommand*\familydefault{\sfdefault}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\section{Taxonomic Resolution Matters for Microbiome-Based
Classification of Colorectal
Cancer}\label{taxonomic-resolution-matters-for-microbiome-based-classification-of-colorectal-cancer}

@@

Courtney R. Armour${^1}$, Begüm D.Topçuoğlu, Andrea Garretto${^1}$,
Patrick D. Schloss ${^1}$${^*}$

@@

${^1}$ Department of Microbiology and Immunology, University of
Michigan, Ann Arbor

@@

${^*}$ Correspondence: Patrick D. Schloss
\href{mailto:pschloss@umich.edu}{pschloss@umich.edu}

@@

Colorectal cancer is one of the most common cancers in men and women and
a leading cause of cancer related deaths in the United States (1). Early
detection and treatment are essential to increase survival rates, but
for a variety of reasons including the invasiveness and high cost of
screening (i.e.~colonoscopy), many people do not comply with recommended
screening guidelines (2) prompting a need for low cost, non-invasive
detection methods. A growing body of research points to the gut
microbiome as a promising target for non-invasive screening to detect
screen relevant neoplasia (SRNs) consisting of pre-cancerous polyps
(i.e.~advanced adenomas) and carcinomas. Efforts to realize the
diagnostic potential of the gut microbiome in detecting SRNs have
focused on machine learning (ML) methods using abundances of operational
taxonomic unit (OTU) classifications based on amplicon sequencing of the
16S rRNA gene \{\}. However, whether this is the optimal taxonomic
resolution for classifying SRNs from microbiome data is unknown.
Additionally, recent work has pushed for the use of amplicon sequence
variants (ASVs) to replace OTUs for marker-gene analysis because of the
improved resolution with ASVs (3). However, whether the additional
resolution provided by ASVs is useful for ML classification is unclear
\{\}. Since ML classification relies on consistent differences between
groups, its possible that the resolution at the ASV level is too
individualized to accurately differentiate groups. Topçuoğlu \emph{et
al} (4) recently demonstrated how to effectively apply machine learning
(ML) methods to microbiome based classification problems and developed a
framework for applying ML practices in a more reproducible way
(mikropml). This analysis utilizes the reproducible framework developed
by Topçuoğlu \emph{et al} to determine which ML method and taxonomic
level produce the best performing classifier for detecting SRNs from
microbiome data.

@@

While comparing AUROC values between models is a useful way to assess
the overall model performance, they summarize the performance across all
thresholds and can be misleading since models with the same AUROC can
have different ROC curve shapes (5). Depending on the intended
implementation of the model, one may want to optimize the true-positive
rate (or sensitivity) over the false-positive rate (or 1-specificity),
or vice versa. In this case, the optimal model will detect as many true
positives (people with SRNs) as possible. To further compare the model
performance across taxonomic levels we compared the sensitivity of the
models at a specificity of 90\%. The highest sensitivity values were
observed for family, genus, and OTU level data (Figure 1B), consistent
with the AUROC results. Phylum, class, order, and ASV sensitivity values
were all significantly lower than family, genus, and OTU sensitivity
values (Figure 1B). This analysis further supports the observation that
finer resolution is does not improve SRN detection.

@@

\subsection{Materials and Methods}\label{materials-and-methods}

@@

\textbf{\emph{Data processing.}} Sequence data was processed with mothur
(1.44.3) using the SILVA reference database (v132) to produce count
tables for phylum, class, order, family, genus, OTU, and ASV following
the Schloss Lab MiSeq SOP described on the mothur website. ASV level
data was also produced using DADA2 to ensure consistent results with a
different pipeline. Data was processed following the DADA2 pipeline, but
setting pool=TRUE to infer ASVs from the whole dataset rather than per
sample. The resulting ASV table was subsampled for consistency with the
mothur data. These results were consistent for ASVs generated with DADA2
(6) (mean AUROC: 0.659).

@@

\subsection{Figures}\label{figures}

\begin{figure}[htbp]
\centering
\includegraphics{figure_1.png}
\end{figure}

@@

\subsection{Tables}\label{tables}

\begin{longtable}[c]{@{}lrrc@{}}
\toprule\addlinespace
Taxonomic Level & Number of Features &
\makecell[c]{Number of Features \\ After Preprocessing} &
\makecell[c]{Percent of Features Kept \\ After Preprocessing}
\\\addlinespace
\midrule\endhead
Phylum & 19 & 9 & 47.4 \%
\\\addlinespace
Class & 36 & 19 & 52.8 \%
\\\addlinespace
Order & 65 & 28 & 43.1 \%
\\\addlinespace
Family & 124 & 54 & 43.5 \%
\\\addlinespace
Genus & 316 & 115 & 36.4 \%
\\\addlinespace
OTU & 20,079 & 705 & 3.5 \%
\\\addlinespace
ASV & 104,106 & 478 & 0.5 \%
\\\addlinespace
\bottomrule
\end{longtable}

@@

\subsection{Supplemental Figures}\label{supplemental-figures}

\begin{figure}[htbp]
\centering
\includegraphics{figure_s1.png}
\end{figure}

@@

\includegraphics{figure_s2.png}\{height=``50\%''\}

@@

\includegraphics{figure_s3.png}\{height=``45\%''\}\\\textbf{Supplemental
Figure 3: Prevalence of Taxa in Samples.} Distribution of the prevalence
of taxa across samples at each taxonomic level. Percent of samples is
split into 10 groups where the first is taxa present in 0 to 10\% of
samples, then \textgreater{}10\% to 20\% of samples, and so on. The
total number of taxa for each taxonomic level after preprocessing is in
parenthesis next to the title of the plot (the name of the taxonomic
level).

@@

\includegraphics{figure_s4.png}\{height=``85\%''\}\\\textbf{Supplemental
Figure 4: Top 10 important taxa at each taxonomic level.} Summary of the
10 most important taxa for the random forest models at each taxonomic
level based on the average decrease in AUROC when the feature is
permuted.

@@

\subsection{References}\label{references}

1. \textbf{{Siegel} R}, \textbf{{Miller} K}, \textbf{{Sauer} A},
\textbf{{Fedewa} S}, \textbf{{Butterly} L}, \textbf{{Anderson} J},
\textbf{{Cercek} A}, \textbf{{Smith} R}, \textbf{{Jemal} A}. 2020.
Colorectal cancer statistics, 2020. CA: A Cancer Journal for Clinicians
\textbf{70}:145--164.
doi:\href{http://dx.doi.org/https://doi.org/10.3322/caac.21601}{https://doi.org/10.3322/caac.21601}.

2. \textbf{{García} G}, \textbf{{Z} A}. 2011. Factors influencing
colorectal cancer screening participation. Gastroenterology Research and
Practice \textbf{2012}:e483417.
doi:\href{http://dx.doi.org/10.1155/2012/483417}{10.1155/2012/483417}.

3. \textbf{{Callahan} B}, \textbf{{McMurdie} P}, \textbf{{Holmes} S}.
2017. Exact sequence variants should replace operational taxonomic units
in marker-gene data analysis. The ISME Journal \textbf{11}:2639--2643.
doi:\href{http://dx.doi.org/10.1038/ismej.2017.119}{10.1038/ismej.2017.119}.

4. \textbf{{Topçuo{ğ}lu} B}, \textbf{{Lesniak} N}, \textbf{{Ruffin} M},
\textbf{{Wiens} J}, \textbf{{Schloss} P}. 2020. A framework for
effective application of machine learning to microbiome-based
classification problems. mBio \textbf{11}.
doi:\href{http://dx.doi.org/10.1128/mBio.00434-20}{10.1128/mBio.00434-20}.

5. \textbf{{Lobo} J}, \textbf{{Jiménez-Valverde} A}, \textbf{{Real} R}.
2008. AUC: a misleading measure of the performance of predictive
distribution models. Global Ecology and Biogeography
\textbf{17}:145--151.
doi:\href{http://dx.doi.org/10.1111/j.1466-8238.2007.00358.x}{10.1111/j.1466-8238.2007.00358.x}.

6. \textbf{{Callahan} B}, \textbf{{McMurdie} P}, \textbf{{Rosen} M},
\textbf{{Han} A}, \textbf{{Johnson} A}, \textbf{{Holmes} S}. 2016.
DADA2: High-resolution sample inference from illumina amplicon data.
Nature Methods \textbf{13}:581--583.
doi:\href{http://dx.doi.org/10.1038/nmeth.3869}{10.1038/nmeth.3869}.
